Gentoo Package Dependencies over Time

### 2014-08-08 Paper/paper.tex
Minor changes to Related Work Section - TEST

In \citet{crowston08} published a comprehensive overview of academical research on open source software development. Of the 184 articles they cite, the vast majority of articles are case studies or surveys, with 4\% of the articles describing the development of empirical instruments and/or measurements. Also, most articles look at the level of a particular group or project, with 4\% looking at the societal level of interacting projects. Crowston et al. find no articles that develop instruments or measurements on the level of OSS packages, which this paper aims to do.

@@

Why this order?

\subsection{Innovation theory}

\subsection{Software innovation}

→ Look for review papers on software innovation and software adoption

\subsection{Innovation theoretic models of adoption}

\subsection{Innovative adoption in software}

>>>>

\subsection{Diffusion of Innovation}

\subsection{ Open Source Software Ecosystems}
In \citet{crowston08} published a comprehensive overview of academical research on open source software development. Of the 184 articles they cite, the vast majority of articles are case studies or surveys, with 4\% of the articles describing the development of empirical instruments and/or measurements. Also, most articles look at the level of a particular group or project, with 4\% looking at the societal level of interacting projects. Crowston et al. find no articles that develop instruments or measurements on the level of OSS packages, which this paper aims to do.

\subsection{Diffusion of Innovation and Adoption in Information Systems}

@@
